Download data

### 2024-02-29 scripts/subsetDataforCrews.Rmd
prototype fn to write out phenology metrics

rm(occ_p. occ_aim)
```

@@

spp_needed <- read.csv('../data/raw/2024sos_species.csv') %>% 
  filter(contract %in% c('SNDO', 'EASTERN MOJAVE')) %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract)

spp_needed <- read.csv('../data/raw/contract_lkp.csv') %>% 
  left_join(spp_needed, ., by = c('contract' = 'Contract_colloquial')) %>% 
  select(-contract)
```

@@

```{r generate projects for crews}

teams_list <- filter(teams, str_detect(Contract, 'SNDO|Eastern Mojave')) %>% 
  split(., f = .$Contract)

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
oppy <- lapply(X = teams_list[1], 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )

tdf <- oppy[[1]] |>
  dplyr::arrange(taxon)

tdf <- dplyr::left_join(tdf, dates[[1]], by = 'doy')

dates <- date_maker()

#names(out_v) <- c('Initation', 'Peak', 'Cessation')
```

>>>>

rm(occ_p, occ_aim)
```

@@

spp_needed <- read.csv('../data/raw/2024sos_species-FIXED.csv') %>% 
  unite('binomial', genus:species) %>% 
  select(binomial, contract)

spp_needed <- read.csv('../data/raw/contract_lkp.csv') %>% 
  left_join(spp_needed, ., by = c('contract' = 'Contract_colloquial')) %>% 
  select(-contract) %>% 
  distinct()
```

@@

```{r}
teams_list <- split(teams, f = teams$Contract)
```

```{r generate projects for crews, eval= F}

@@

spp_needed <- rename(spp_needed, taxon = binomial)
p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(X = teams_list, 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )
